### 2011-01-11 doc/tech_doc/xrsl/xrsl-gm.tex
Finalising porting "as is" of 4 documents from arc0 to arc1 tree

  \phantomsection
  \index{XRSL:attribute:sstdin}\addcontentsline{toc}{subsection}{sstdin}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{sstdin}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC $\leq$ 0.5.25}
  \begin{tabular}{lp{13cm}}
    User input:&\verb##\\
    GM input:&\verb#(sstdin=<filename>)#\\
    Example:&\verb#(sstdin="myinput.dat")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:action}\addcontentsline{toc}{subsection}{action}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{action}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb##\\
    GM input:&\verb#(action="request"|"cancel"|"clean")#\\
    Example:&\verb#(action="request")#\\
  \end{tabular}

  Action to be taken by the gatekeeper: submit the job, cancel job
  execution, or clear the results of the job (also cancels the job).

  \phantomsection
  \index{XRSL:attribute:savestate}\addcontentsline{toc}{subsection}{savestate}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{savestate}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC $\leq$ 0.5.25}
  \begin{tabular}{lp{13cm}}
    User input:&\verb##\\
    GM input:&\verb#(savestate="yes"|"no")#\\
    Example:&\verb#(savestate="yes")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:lrmstype}\addcontentsline{toc}{subsection}{lrmstype}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{lrmstype}
  \end{shaded}
  \versions{ARC $\leq$ 0.3.15}
  \begin{tabular}{lp{13cm}}
    User input:&\verb##\\
    GM input:&\verb#(lrmstype=<string>)#\\
    Example:&\verb#(lrmstype="pbs")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:hostName}\addcontentsline{toc}{subsection}{hostName}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{hostName}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb##\\
    GM input:&\verb#(hostname=<string>)#\\
    Example:&\verb#(hostName="grid.quark.lu.se")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:jobid}\addcontentsline{toc}{subsection}{jobid}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{jobid}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb##\\
    GM input:&\verb#(jobid=<string>)#\\
    Example:&\verb#(jobid="grid.quark.lu.se:2119/jobmanager-ng/157111017133827")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:clientxrsl}\addcontentsline{toc}{subsection}{clientxrsl}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{clientxrsl}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.28, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb##\\
    GM input:&\verb#(clientxrsl=<string>)#\\
    Example:&\verb#(clientxrsl="&(executable=/bin/echo)(arguments=boo)")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:clientsoftware}\addcontentsline{toc}{subsection}{clientsoftware}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{clientsoftware}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.35, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb##\\
    GM input:&\verb#(clientsoftware=<string>)#\\
    Example:&\verb#(clientsoftware="nordugrid-arc-0.5.39")#\\
  \end{tabular}

>>>>

  \phantomsection
  \index{XRSL:attribute:sstdin}\addcontentsline{toc}{subsection}{sstdin}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{sstdin}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC $\leq$ 0.5.25}
  \begin{tabular}{lp{13cm}}
    GM input:&\verb#(sstdin=<filename>)#\\
    Example:&\verb#(sstdin="myinput.dat")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:action}\addcontentsline{toc}{subsection}{action}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{action}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    GM input:&\verb#(action="request"|"cancel"|"clean"|"renew"|"restart")#\\
    Example:&\verb#(action="request")#\\
  \end{tabular}

  Action to be taken by the gatekeeper: submit the job, cancel job
  execution, clear the results of the job (also cancels the job),
  renew the proxy of the job, or restart the job from a previous
  failed state.

  \phantomsection
  \index{XRSL:attribute:savestate}\addcontentsline{toc}{subsection}{savestate}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{savestate}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC $\leq$ 0.5.25}
  \begin{tabular}{lp{13cm}}
    GM input:&\verb#(savestate="yes"|"no")#\\
    Example:&\verb#(savestate="yes")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:lrmstype}\addcontentsline{toc}{subsection}{lrmstype}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{lrmstype}
  \end{shaded}
  \versions{ARC $\leq$ 0.3.15}
  \begin{tabular}{lp{13cm}}
    GM input:&\verb#(lrmstype=<string>)#\\
    Example:&\verb#(lrmstype="pbs")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:hostName}\addcontentsline{toc}{subsection}{hostName}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{hostName}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    GM input:&\verb#(hostname=<string>)#\\
    Example:&\verb#(hostName="grid.quark.lu.se")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:jobid}\addcontentsline{toc}{subsection}{jobid}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{jobid}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    GM input:&\verb#(jobid=<string>)#\\
    Example:&\verb#(jobid="grid.quark.lu.se:2119/jobmanager-ng/157111017133827")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:clientxrsl}\addcontentsline{toc}{subsection}{clientxrsl}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{clientxrsl}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.28, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    GM input:&\verb#(clientxrsl=<string>)#\\
    Example:&\verb#(clientxrsl="&(executable=/bin/echo)(arguments=boo)")#\\
  \end{tabular}

@@

  \phantomsection
  \index{XRSL:attribute:clientsoftware}\addcontentsline{toc}{subsection}{clientsoftware}
  \hspace*{0.5cm}
  \begin{shaded}
    \xrsl{clientsoftware}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.35, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    GM input:&\verb#(clientsoftware=<string>)#\\
    Example:&\verb#(clientsoftware="nordugrid-arc-0.5.39")#\\
  \end{tabular}
